Resource Buying Games

### 2017-03-02 paper.tex
started alg

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing. The algorithm
we present in the following chooses a basis for every player by iteratively
adding one element from a cut and contracting the matroid to the added element
while deleting all other elements from the cut. Since cuts are inclusion-wise
minimal deleting all but one element from one cut leaves at least one possible
basis for the player available.

>>>>

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing. The algorithm
we present in the following chooses a basis for every player by iteratively
adding one element from a cut and contracting the matroid to the added element
while deleting all other elements from the cut. Since cuts are inclusion-wise
minimal deleting all but one element from one cut leaves at least one possible
basis for the player available. For every player we maintain the elements which
are chosen for her up to the current state (\emph{working basis}) and which
elements are still available to build her basis (\emph{ground-set}) and which
bases she can still use. Initially the working basis is empty and the
ground-set and available bases are taken from the matroid of the player. For
every resource we maintain the cost the next added load causes and how much
load already is placed upon the resource(\emph{current load}). Initially for
every resource $e$ the current load is zero and the next load causes $c_{e}(1)$
cost.
